### 2025-07-28 README.Rmd
Fix URL

**hatchR** is an R package for predicting hatch and emergence timing for a wide range of wild fishes using the effective value framework (Sparks et al., (2019) <DOI:10.1139/cjfas-2017-0468>). **hatchR** offers users access to established phenological models and the flexibility to incorporate custom parameterizations using external datasets. The package includes functions for model selection, phenology prediction, and visualization. **hatchR** is designed to be user-friendly and accessible to a wide range of users, including researchers, managers, and educators.

@@

## Interactive Shiny App <img src='https://upload.wikimedia.org/wikipedia/commons/b/bf/Shiny_hex_logo.svg' align="right" height="50" />

>>>>

**hatchR** is an R package for predicting hatch and emergence timing for a wide range of wild fishes using the effective value framework (Sparks et al., 2019, *Canadian Journal of Fisheries and Aquatic Sciences*, 76(1): 123-135). **hatchR** offers users access to established phenological models and the flexibility to incorporate custom parameterizations using external datasets. The package includes functions for model selection, phenology prediction, and visualization. **hatchR** is designed to be user-friendly and accessible to a wide range of users, including researchers, managers, and educators.

A manuscript accompanying this package is *in press* at *Fisheries*, forthcoming this Fall.

@@

## Interactive Shiny App
